Wealth dynamics in the presence of\\network structure and primitive cooperation

### 2019-07-23 manuscript/specnet_conffmt.tex
Change author order.
Update conference header.

%Conference
\acmConference[CSS'18]{ACM Computational Social Science conference}{July 1997}{El
  Paso, Texas USA}
\acmYear{2018}
\copyrightyear{2018}

@@

\begin{document}
\title{Wealth dynamics in the presence of network structure and primitive cooperation}
%\titlenote{Produces the permission block, and
 % copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
 % \texttt{acmart.pdf} document}

\author{Stephen Davies}
\affiliation{%
  \institution{University of Mary Washington}
  \streetaddress{1301 College Avenue}
  \city{Fredericksburg}
  \state{Virginia}
  \postcode{22401}
}
\email{stephen@umw.edu}

>>>>

%Conference
\acmConference[CSS'19]{CSSSA's Annual Conference on Computational Social
Science}{October 24--27, 2019}{Santa Fe, NM, USA}
\acmYear{2019}

\copyrightyear{2019}

@@

\begin{document}
\title{Wealth dynamics in the presence of\\network structure and primitive cooperation}
%\titlenote{Produces the permission block, and
 % copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
 % \texttt{acmart.pdf} document}

\author{Stephen Davies}
\affiliation{%
  \institution{University of Mary Washington\\Department of Computer Science}
  \streetaddress{1301 College Avenue}
  \city{Fredericksburg}
  \state{Virginia}
  \postcode{22401}
}
\email{stephen@umw.edu}
